---
title: Notes On Everything
author: Desmond Tuiyot
date: '2020-05-24'
slug: notes-on-everything
categories:
  - Statistics
  - Personal Notes
tags:
  - Data Analysis
  - Notes
  - Random
bibliography: ref.bib
# csl: style.csl 
---

```{r include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

## Statistics {#statistics}

## Probability {#probability}

## Machine Learning {#machine_learning}

## Algorithms & Data Structures {#algos_data_structures}

## Python

## RShiny

### 1. Inputs & Outputs
#### Inputs
```
textInput()
sliderInput()
selectInput()
numericalInput()
dateRangeInput()
```

all inputs have the format

```{r echo=FALSE, eval=FALSE}
library(shiny)
library(dplyr)
library(tidyr)
```
``` {r eval=FALSE}
__input("inputId",
        "label",
        unique_param1, unique_param2, ...)
```


#### Render Functions
Render functions are used to built outputs in the server based on
inputs and possibly other stuff

```{r eval=FALSE}
renderText()
renderTable()
renderImage()
renderPlot()
```

#### Output Functions
Output functions are used in the ui to display the result built by 
render functions in the server

```{r eval=FALSE}
textOutput()`
plotOutput()
tableOutput() or dataTableOutput()
imageOutput()
```

##### Non-shiny output and render functions
DT, leaflet, and plotly -> interactive data tables, maps, and plots as Shiny outputs

In order to add an output to a Shiny app, we need to:

1. Create the output -> could be a plot, table, string, etc
2. Render the output in the `server` function using appropriate `Render___` function.
3. Assign this render to a variable name prefixed with `output$___`
3. Use the corresponding `___Output` and pass in the variable name

### Layouts and Themes

#### Layouts

1. Sidebar layouts
```{r eval = FALSE}
sidebarLayout(
  sidebarPanel(insert input/output here),
  mainPanel(insert input/output here)
)
```

2. Tab layouts
```{r eval=FALSE}
sidebarLayout(
  sidebarPanel(insert input/output here),
  mainPanel(
    
    tabsetPanel(
      tabPanel(),
      tabPanel()
    )
  )
)
```

#### Themes
Add a theme selector to your Ui
```{r eval=FALSE}
shinythemes::themeSelector()
```
Then you can add it to your Ui

#### Building The App: A Process

1. Add inputs to the `ui()`
2. Add outputs to the `ui()`/`server()`
3. Modify the app layout in the `ui()`
4. Update the output in the `server()` to incorporate the input

### Reactive Programming  
#### Reactivity 101  
1. Reactive Sources  
Often input widgets on a browser - `textInput`, `textOutput`, and so on  
Can be connected to multiple endpoints
2. Reactive Endpoints  
Inputs such as plots or tables that show some result and is connected to a reactive source  
An example of this are  observers. THe `render__` family of functions are observers. They generate reactive expressions, which when assigned to a reactive source, are turned into observers
3. Reactive Conductors  
These wrap around a computation that may be repeatedly evaluated. An implementation of this is: Reactive Expressions    
These are similar to functions but are lazily loaded and cached.

#### Reactives vs Observers  
* `reactive()` calculates values, with no side effects
* `observe()` performs actions, with side effects

* **Key Differences:**  
  + Reactives return a value, while observers do not return any value
  + Reactives are lazily loaded, observers eagerly respond to changes in their dependencies
  + Observers are used primarily for their side effects, while reactives must not have side effects

#### Stop-delay-trigger shiny actions  
**Isolate** - By default, any changes to inputs automatically updates the dependent outputs  
We can use `isolate()` to make sure that the output does not automatically update
when the input changes- we wrap the reactive value like so 
```{r eval=FALSE}
isolate(input$___)
```  
**Trigger** - When we want to trigger an action in response to some event, we create reactive expressions using `eventReactive` like below. 
```{r eval=FALSE}
rv<-eventReactive(event_to_react_to(could be a button),
                  output)
```
If you want to perform an action in response to an event, use `observeReactive`
```{r eval=FALSE}
rv<-eventReactive(event_to_react_to,
                  action)
```

#### Other Stuff.  
1. To show an error message, wrap the input inside  a `need` function, wrapped around a `validate` function. 
```{r eval=FALSE}
render___({
  validate(
    need(input$param_name, "Error message")
  )
})
```
2. `shinyWidgets` is a package that provides a function `shinyWidgetsGallery()` which opens up a custom app that shows example inputs and corresponding code that you can incorporate into your app 



## References {#references}
